Online resolving assembly graph by ONT long reads data

### 2019-10-29 paper.tex
adding more results

\begin{figure}[!hpt]
\centering
\subfloat[Initial graph]{
	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_0.png}
}
\hfill
\subfloat[Resolved graph]{
	\includegraphics[width=.45\textwidth]{images/npgraph_shigella_2.png}
}
\caption[Assembly graph resolving on \npgraph{} Graph View]{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View. The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
\label{F:npgraph_graphview}
\end{figure}

Figure~\ref{F:npgraph_graphview} shows an example of the real-time graph resolving process being displayed on GUI.
The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
Smaller fragments, even unfinished but with high remaining coverage, are also presented as potential candidates for further downstream analysis.
Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
Assembly graph is the data structure describing the assembly process at a lower level of more details.
The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block of the assembly construction method (\npgraph{}).

>>>>

\subsection*{Scaffolding metagenomics data set}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Conclusions}
Assembly graph is the data structure describing the assembly process at a lower level of more details.
The current chapter brings this informative knowledge to the original \npscarf{}'s mechanism in two ways, either partly for the gap-filling module only (\npscarfg{}) or completely as the building block of the assembly construction method (\npgraph{}).
